\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[usenames, dvipsnames]{color}
\title{Influential Investment Prediction: Project Proposal}
\author{Lingrui Li (ll829), Joyce Chen (cc2626), Aleah Kennedy (ack237)}
\begin{document}
\maketitle
\section*{Abstract}
In the world of finance, there are companies and people who have the capital to influence stock prices directly by investing heavily in other firms. However, we have noticed a trend where these companies stock prices rise beyond what can be directly attributed to the investment in the six months following the investment. We aim to explore this trend by modeling stock prices' reactions to large investments by Goldman Sachs. Particularly, we will attempt to predict whether a large investment in a company by Goldman Sachs will lead to gains over both the following quarter, and the quarter after that.

\section*{Benefits}
With the information obtained from this model, we can predict with greater accuracy the behavior of stocks after influential investments. Such a model, once established, can be extended to other influential investment banks or individuals to give smaller investors greater insight into the feature behavior of stocks. Datasets on other companies and individuals will be available through the public domain 13-F documents from the Security and Exchange Commissions so the applications of the study will be widespread.

\section*{Data Collection Methods} 
We will be needing two types of data: 
\begin{itemize}
\item Data on quarterly holdings by Goldman Sachs in various companies
\item Data on quarterly performance of the companies invested in
\end{itemize}

We are collecting our holdings data from the Security and Exchange Commission's public 13-F-HR/A forms for Goldman Sachs Group Incorporated, and our performance data from Yahoo finance and Bloomberg. 
\section*{Feasibility}
We have established the data collection points for this research already, which we anticipate to be the most difficult aspect. Compiling the data from the SEC files can be automated, making the collection of performance data from Yahoo Finance the bottleneck of the process. We will be limiting our exploration to companies which Goldman Sachs has invested at least 1 million, so the required data collection will be within human confines. By working as a team, we expect to be able to complete quarterly performance data within the next two weeks.
\end{document}
